Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
typo

We investigate two different approaches of integrating solution generalisation 
with CEGIS:
\begin{itemize}
\item[1.] The first approach uses abstract acceleration to compute the set of reachable states,
  which enables it to perform abstraction refinement inside the CEGIS loop (see Sec~\ref{sec:CEGIS-abstraction-refinement}). 
\todo{Dario, can you briefly explain solution generalisation for your approach?}
\item[2.] The second approach uses a multi-staged validation phase
  and performes solution generalisation based on
the plant's precision, the number of loop unrollongs
and the sampling rate (see Sec.~\ref{sec:CEGIS-precision-incrementation}).
%%   relies on computing a 
%% completeness threshold $k$ for each loop such that it is sufficient to 
%% unroll the corresponding loop $k$ times. For this approach the 
%% generalisation step is given as an incremental
%% increase of precision and sampling rate 
\end{itemize}

>>>>

We investigate two different approaches of integrating solution generalisation 
with CEGIS:
\begin{itemize}
\item[1.] The first approach uses abstract acceleration to compute the set of reachable states,
  which enables it to perform abstraction refinement inside the CEGIS loop (see Sec~\ref{sec:CEGIS-abstraction-refinement}). 
\todo{Dario, can you briefly explain solution generalisation for your approach?}
\item[2.] The second approach uses a multi-staged validation phase
  and performes solution generalisation based on
the plant's precision, the number of loop unrollings
and the sampling rate (see Sec.~\ref{sec:CEGIS-precision-incrementation}).
%%   relies on computing a 
%% completeness threshold $k$ for each loop such that it is sufficient to 
%% unroll the corresponding loop $k$ times. For this approach the 
%% generalisation step is given as an incremental
%% increase of precision and sampling rate 
\end{itemize}
